---
title: "Project 4 - Collaborative Filtering Algorithms Evaluation"
author: "Group 9"
date: "Spring 2018"
output: pdf_document
---

# Memory-based Algorithm

## Load and process the data

```{r}
## Load data
MStrain <- read.csv("../data/MS_sample/data_train.csv")
MStest  <- read.csv("../data/MS_sample/data_test.csv")
Movietrain <- read.csv("../data/eachmovie_sample/data_train.csv")
Movietest  <- read.csv("../data/eachmovie_sample/data_test.csv")

## Data Processing

# Using function in Process_Data.R to transform the dataset.

# source("../lib/Process_Data.R")
# Movie_train <- Movie_data(Movietrain)
# Movie_test  <- Movie_data(Movietest)
# save(Movie_train, file = "../output/data/Movie_train.RData")
# save(Movie_test, file = "../output/data/Movie_test.RData")


# Here, we directly load the processed dataset.

load("../output/data/MS_train.RData")
load("../output/data/Movie_train.RData")
load("../output/data/MS_test.RData")
load("../output/data/Movie_test.RData")
```

## Similarity Weight

### 1. Pearson Correlation
We will directly load our data into this file.
```{r}
# source("../lib/Pearson_MeanSquare.R")

## MS Data

# weight_pearson_MS <- cor(t(MS_train), method = "pearson")
# save(weight_pearson_MS, file = "../output/Similarity_Weight/weight_pearson_MS.RData")
load("../output/Similarity_Weight/weight_pearson_MS.RData")

## Movie Data

# weight_pearson_Movie <- cor(t(Movie_train), method = "pearson", use = "pairwise.complete.obs")
# save(weight_pearson_Movie, file = "../output/Similarity_Weight/weight_pearson_Movie.RData")
load("../output/Similarity_Weight/weight_pearson_Movie.RData")
```

### 2. Mean-squared-difference
```{r}
## MS Data

# weight_MSD_MS <- MSD(MS_train)
# save(weight_MSD_MS, file = "../output/Similarity_Weight/weight_MSD_MS.RData")
load("../output/Similarity_Weight/weight_MSD_MS.RData")

## Movie Data

# Without Intersection
# weight_MSD_Movie <- MSD(Movie_train)
# save(weight_MSD_Movie, file = "../output/Similarity_Weight/weight_MSD_Movie.RData")
load("../output/Similarity_Weight/weight_MSD_Movie.RData")
```

### 3. SimRank
```{r}
# source("../lib/Simrank.R")
# 
# reg.sim_mat <- simrank_regular(Movie_train, maxIteration = 30, C1 = 0.8)
# users <- reg.sim_mat[[2]]
# save(simrank_Movie, file="../output/simrank_Movie.RData")
load("../output/simrank_Movie.RData")

# adv.sim_mat <- simrank_adv(Movie_train, maxIteration = 30, C1 = 0.8)
# simrank_Movie_p <- adv.sim_mat[[2]]
# simrank_Movie_n <- adv.sim_mat[[5]]
# save(simrank_Movie_p, file="../output/simrank_Movie_positive.RData")
# save(simrank_Movie_n, file="../output/simrank_Movie_negative.RData")

# Movie_train[is.na(Movie_train)] <- 0
# n_users <- nrow(Movie_train)
# n_movies <- ncol(Movie_train)
# nodesnum <- n_users + n_movies
# 
# Movie_train_p <- Movie_train - 3
# Movie_train_p[Movie_train_p < 0] <- 0
# Movie_train_n <- -(Movie_train - 4)
# Movie_train_n[Movie_train_n<0 | Movie_train_n == 4] <- 0
# save(Movie_train_p, file = "../output/data/Movie_train_p.RData")
# save(Movie_train_n, file = "../output/data/Movie_train_n.RData")

load("../output/data/Movie_train_p.RData")
load("../output/data/Movie_train_n.RData")
load("../output/simrank_Movie_postive.RData")
load("../output/simrank_Movie_negative.RData")

```

## Variance Weighting 
```{r}
# source("../lib/var_weight.R")
# 
# var_weight_MS <- var_weight_matrix(mat = MS_train)
# var_weight_MS[is.na(var_weight_MS)] = 0
# var_weight_MS <- round(var_weight_MS,3)
# save(var_weight_MS, file = "../output/variance_weight/var_weight_MS.RData")
load("../output/variance_weight/var_weight_MS.RData")
 
# var_weight_Movie <- var_weight_matrix(mat = Movie_train)
# var_weight_Movie[is.na(var_weight_Movie)] = 0
# var_weight_Movie <- round(variance_weight_Movie,3)
# save(var_weight_Movie, file = "../output/variance_weight/var_weight_Movie.RData")
load("../output/variance_weight/var_weight_Movie.RData")
```

## Selecting Neighborhoods

### Best-n neighbors & Prediction
```{r}
source("../lib/neighbor&predict.R")
# MS Data:
# Pearson
pearson_MS_neighbor = neighbors.select(weight_pearson_MS, N=20)
pearson_MS_pred = predict.MS(sim_weights = weight_pearson_MS, 
                             top.neighbors = pearson_MS_neighbor)

# MSD
MSD_MS_neighbor = neighbors.select(weight_MSD_MS, N=20)
MSD_MS_pred = predict.MS(sim_weights = weight_MSD_MS, 
                             top.neighbors = MSD_MS_neighbor)

# Pearson + Var
pearson_var_MS = var_weight_MS * weight_pearson_MS
pearson_var_MS_neighbor = neighbors.select(pearson_var_MS,N=20)
pearson_var_MS_pred = predict.MS(sim_weights =pearson_var_MS, 
                                 top.neighbors = pearson_var_MS_neighbor)

# MSD + Var
MSD_var_MS = var_weight_MS * weight_MSD_MS
MSD_var_MS_neighbor = neighbors.select(MSD_var_MS,N=20)
MSD_var_MS_pred = predict.MS(sim_weights =MSD_var_MS, 
                                 top.neighbors = MSD_var_MS_neighbor)

# Movie Data:
# Pearson
pearson_Movie_neighbor =  neighbors.select(weight_pearson_Movie, N=20)
pearson_Movie_pred = predict.Movie(sim_weights = weight_pearson_Movie,
                                   top.neighbors = pearson_Movie_neighbor)

# MSD
MSD_Movie_neighbor =  neighbors.select(weight_MSD_Movie, N=20)
MSD_Movie_pred = predict.Movie(sim_weights = weight_MSD_Movie,
                                   top.neighbors = MSD_Movie_neighbor)

# Regular SimRank
simrank_Movie_neighbor =  neighbors.select(as.matrix(simrank_Movie), N=20)
simrank_pred = predict.Movie(sim_weights = as.matrix(simrank_Movie),
                                    top.neighbors = simrank_Movie_neighbor)

# Improved SimRank
simrank_Movie_neighbor_p = neighbors.select(as.matrix(simrank_Movie_p), N=20)
simrank_pred_p = predict.Movie(sim_weights = as.matrix(simrank_Movie_p), train = Movie_train_p, top.neighbors = simrank_Movie_neighbor_p)

Movie_train_n[Movie_train_n!=0 & !is.na(Movie_train_n)] <- 4 - Movie_train_n[Movie_train_n!=0 & !is.na(Movie_train_n)]
simrank_Movie_neighbor_n = neighbors.select(as.matrix(simrank_Movie_n), N=20)
simrank_pred_n = predict.Movie(sim_weights = as.matrix(simrank_Movie_n), train = Movie_train_n, top.neighbors = simrank_Movie_neighbor_n)

simrank_pred_np <- simrank_pred_n + simrank_pred_p 


# Pearson + Var
pearson_var_Movie = var_weight_Movie * weight_pearson_Movie
pearson_var_Movie_neighbor =  neighbors.select(pearson_var_Movie, N=20)
pearson_var_Movie_pred = predict.Movie(sim_weights = pearson_var_Movie,
                                       top.neighbors = pearson_var_Movie_neighbor)

# MSD + Var
MSD_var_Movie = var_weight_Movie * weight_MSD_Movie
MSD_var_Movie_neighbor =  neighbors.select(MSD_var_Movie, N=20)
MSD_var_Movie_pred = predict.Movie(sim_weights = MSD_var_Movie,
                                       top.neighbors = MSD_var_Movie_neighbor)

# SimRank + Var
simrank_var_Movie = var_weight_Movie * simrank_Movie
simrank_var_Movie_neighbor =  neighbors.select(simrank_var_Movie, N=20)
simrank_var_Movie_pred = predict.Movie(sim_weights = simrank_var_Movie,                                                             top.neighbors = simrank_var_Movie_neighbor)

```

# Model-based Algorithms(Cluster Model)
```{r message=FALSE, warning=FALSE}
#install.packages(c("plyr","doSNOW","mixtools"))
library(plyr)
library(doSNOW)
library(mixtools)
source("../lib/clustering_model.R")
source("../lib/Evaluation.R")
```

## Cross Validation to choose number of cluster
```{r,eval=FALSE}
train_set <- MS_train
val_set <- matrix(0,nrow=nrow(train_set), ncol=ncol(train_set))
set.seed(10)

for(i in 1:nrow(train_set)){
  idx <- as.numeric(unlist(which(train_set[i,] == 1)))
  val_idx <- sample(idx,round(length(idx))*0.2)
  train_set[i,val_idx] <- 0
  val_set[i,val_idx] <- 1
}

val_score <- c()
n_cluster <- seq(5,40,5)

for (nc in n_cluster){
  cluster_model <- MultmixEM(train_set, navie=F,C=nc,epsilon=1e-05)
  cluster_model_pred <- cluster_predict_MS(train_set, cluster_model$gamma, cluster_model$mu)
  val_score <- c(val_score,rank_score(cluster_model_pred, val_set))
}

```

```{r}
val_score <- c(35.66253, 36.79171, 37.85963, 38.0627, 38.15919, 38.51203, 39.22749, 38.82844)
```

```{r,warning=FALSE}
# train
cluster_model <- MultmixEM(MS_train, navie=F,C=35)
save(cluster_model, file="../output/cluster_model/cluster_model.R")

# predict
cluster_model_pred <- cluster_predict_MS(MS_train, cluster_model$gamma, cluster_model$mu)
save(cluster_model_pred, file="../output/cluster_model/cluster_model_pred.R")
```

```{r}
# load saved parameters and predictions
load("../output/cluster_model/cluster_model.R")
load("../output/cluster_model/cluster_model_pred.R")
```

# Evaluation 
```{r}
source("../lib/Evaluation.R")
```

### MS Dataset
### Rank Score on train set
```{r}
pearson_rankscore_MS_tr <- rank_score(pearson_MS_pred, MS_train)
pearson_var_rankscore_MS_tr <- rank_score(pearson_var_MS_pred, MS_train)

MSD_rankscore_MS_tr <- rank_score(MSD_MS_pred, MS_train)
MSD_var_rankscore_MS_tr <- rank_score(MSD_var_MS_pred, MS_train)

cluster_model_MS_tr <- rank_score(cluster_model_pred, MS_train)

pearson_rankscore_MS_tr
pearson_var_rankscore_MS_tr
MSD_rankscore_MS_tr
MSD_var_rankscore_MS_tr
cluster_model_MS_tr 
```
### Rank Score on test set
```{r}
pearson_rankscore_MS <- rank_score(pearson_MS_pred, MS_test)
pearson_var_rankscore_MS <- rank_score(pearson_var_MS_pred, MS_test)

MSD_rankscore_MS <- rank_score(MSD_MS_pred, MS_test)
MSD_var_rankscore_MS <- rank_score(MSD_var_MS_pred, MS_test)

cluster_model_MS <- rank_score(cluster_model_pred, MS_test)

pearson_rankscore_MS
pearson_var_rankscore_MS
MSD_rankscore_MS
MSD_var_rankscore_MS
cluster_model_MS
```

### EachMovie Dataset
### MAE
```{r}
pearson_MAE_Movie <- MAE(pearson_Movie_pred, Movie_test)
pearson_var_MAE_Movie <- MAE(pearson_var_Movie_pred, Movie_test)

MSD_MAE_Movie <- MAE(MSD_Movie_pred, Movie_test)
MSD_var_MAE_Movie <- MAE(MSD_var_Movie_pred, Movie_test)

simrank_MAE_Movie <- MAE(simrank_pred, Movie_test)
simrank_MAE_Movie_np <- MAE(simrank_pred_np, Movie_test)
simrank_var_MAE_Movie <- MAE(simrank_var_Movie_pred, Movie_test)

pearson_MAE_Movie
pearson_var_MAE_Movie
MSD_MAE_Movie
MSD_var_MAE_Movie
simrank_MAE_Movie
simrank_MAE_Movie_np
simrank_var_MAE_Movie
```

### ROC_4
```{r}
pearson_ROC_4_Movie <- ROC_4(pearson_Movie_pred, Movie_test)
pearson_var_ROC_4_Movie <- ROC_4(pearson_var_Movie_pred, Movie_test)

MSD_ROC_4_Movie <- ROC_4(MSD_Movie_pred, Movie_test)
MSD_var_ROC_4_Movie <- ROC_4(MSD_var_Movie_pred, Movie_test)

# simrank_ROC_4_Movie <- ROC_4(simrank_Movie_pred, Movie_test)
# simrank_var_ROC_4_Movie <- ROC_4(simrank_var_Movie_pred, Movie_test)

pearson_ROC_4_Movie
pearson_var_ROC_4_Movie
MSD_ROC_4_Movie
MSD_var_ROC_4_Movie
#simrank_ROC_4_Movie
#simrank_var_ROC_4_Movie
```


